%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\vspace{-1.0mm}
\cvsection{Experience}
\vspace{-2.0mm}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
\setlength{\extrarowheight}{2mm}

%---------------------------------------------------------
%---------------------------------------------------------
\cventry
    {Software Eng Lead - Computer Vision} % Job title
    {Kurtz Robotics} % Organization
    {Boston, MA} % Location
    {Jan 2025 - May 2025} % Date(s)
    {
    \begin{cvitems}
      \item {Led development of AI-powered tomato ripeness detection system achieving \textbf{99.24\%} accuracy using \textbf{EfficientNetV2-S} deep learning model.}
      \item {Designed computer vision pipeline with \textbf{Intel RealSense D456} cameras for real-time RGB-D image processing and 3D object analysis.}
      \item {Built cross-platform training system using \textbf{PyTorch Lightning} with GPU acceleration support for CUDA, ROCm, and Apple Silicon.}
      \item {Developed lighting-adaptive model simulation to ensure robust performance across varying agricultural field conditions.}
      \item {Created \textbf{Flask} REST API for real-time image capture and processing, integrating seamlessly with robotic harvesting systems.}
    \end{cvitems}
    }

\vspace{2mm}
%---------------------------------------------------------
\cventry
    {Research Assistant - \href{https://users.soe.ucsc.edu/~qian/}{\uline{Dr. Chen Qian}}} % Job title
    {Disaggregated HNSW Lab} % Organization
    {Baskin Engineering, UCSC} % Location
    {Oct 2024 - Present} % Date(s)
    {
        \begin{cvitems}
        \item {Designed Pyramid Search, a hierarchical vector search system using \textbf{HNSW} indexing that achieves \textbf{99.79\%} recall accuracy.}
        \item {Built Meta-HNSW routing system for distributing search queries intelligently across partitioned vector databases.}
        \item {Developed high-performance \textbf{C++/FAISS} integration with graph partitioning, processing 10,000+ queries per second.}
        \item {Optimized memory usage for similarity search operations on large-scale, high-dimensional vector datasets.}
        \item {Created comprehensive benchmarking framework using SIFT datasets to evaluate search accuracy versus speed performance.}
        \end{cvitems}
    }

\vspace{2mm}
%---------------------------------------------------------
\cventry
    {Ray Distributed Systems Researcher - Dr. Liting Hu} % Job title
    {ELVES Lab} % Organization
    {Baskin Engineering, UCSC} % Location
    {Jul 2024 - Oct 2024} % Date(s)
    {
      \begin{cvitems}
        \item {Built fault-tolerant task scheduling system for \textbf{Ray v2} using \textbf{C++}, reducing recovery time through predictive task replication.}
        \item {Optimized distributed memory management by improving reference counting, resolving object storage bottlenecks in large-scale clusters.}
        \item {Enhanced task failure recovery mechanisms, significantly improving system reliability for production machine learning workflows.}
      \end{cvitems}
    }

\vspace{2mm}
%---------------------------------------------------------
\cventry
    {Full Stack Developer Intern} % Job title
    {TouchBase Inc.} % Organization
    {Seattle, WA} % Location
    {Jul 2023 - Sep 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed scalable \textbf{Node.js/Koa} REST APIs deployed on \textbf{Microsoft Azure Functions} for serverless, event-driven web applications.}
        \item {Optimized \textbf{MySQL} database performance by redesigning schema structure, improving query indexing and data normalization.}
        \item {Delivered 10+ responsive front-end features using \textbf{HTML/CSS} in collaboration with design and product teams, handling complex edge cases.}
      \end{cvitems}
    }
%---------------------------------------------------------
\end{cventries}
