%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}
\vspace{-3.0mm}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
\setlength{\extrarowheight}{2mm}

%---------------------------------------------------------
\cventry
    {\textbf{\href{https://github.com/howwyhoward/FastServe}{FastServe} - AI Inference System}} % Project title 
    {} % Empty
    {} % Empty
    {Jun 2025 - Present} % Date
    { % Description  
        \begin{cvitems}
            \item {Built FastServe AI inference server implementing \textbf{Multi-Level Feedback Queue (MLFQ)} algorithm with intelligent job profiling and dynamic queue assignment for optimized request scheduling.}
            \item {Designed \textbf{HuggingFace Transformers} backend with Apple Silicon (MPS) optimization, memory management, and key-value cache system for high-performance AI inference.}
            \item {Achieved \textbf{95\%} success rate in comprehensive performance evaluation with real-time server management capabilities.}
        \end{cvitems}  
    }

\vspace{2mm}
%---------------------------------------------------------
\cventry  
    {\textbf{\href{https://github.com/khanna-parth/MapsProject}{Waypoint} - Realtime Party Navigation}} % Project title  
    {} % Empty
    {} % Empty
    {Jan 2025 - Apr 2025} % Date  
    { % Description  
        \begin{cvitems}  
            \item {Developed scalable backend with \textbf{PostgreSQL} and \textbf{TypeORM}, enabling efficient data handling for user and location management.}  
            \item {Implemented \textbf{WebSocket} connections for real-time location sharing and group coordination, enhancing collaborative navigation.}  
            \item {Integrated \textbf{Google Maps API} for optimized route planning, turn-by-turn directions, and location-based query performance.} 
            \item {Containerized application using \textbf{Docker} and added thread-safe operations with async-mutex to prevent concurrent update conflicts.}   
        \end{cvitems}  
    }

\vspace{2mm}
%---------------------------------------------------------
\cventry
    {\textbf{\href{https://github.com/howwyhoward/Diligent}{Diligent} - Messenger App}} % Project title
    {} % Empty
    {} % Empty
    {Jul 2024 - Sep 2024} % Date
    { % Description  
        \begin{cvitems}
            \item {Built a full-stack messaging application using \textbf{Node.js}, \textbf{Express}, \textbf{React}, and \textbf{PostgreSQL} with real-time chat functionality.}
            \item {Implemented secure user authentication with \textbf{JWT} tokens and session management, storing user data in optimized \textbf{JSONB format}.}
            \item {Designed responsive UI components with \textbf{Material-UI} and achieved 95\% test coverage using \textbf{React Testing Library} for component testing.}
            \item {Created comprehensive \textbf{RESTful APIs} documented with OpenAPI 3.0 and containerized the entire application using \textbf{Docker}.}
        \end{cvitems}  
    }
%---------------------------------------------------------
\end{cventries}
